Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach

### 2016-06-03 sections0.03/data0.03.tex
PB edited data section, added important comment

\section{DATA}
\label{sec: data}
We use SED templates from K96 to train neural networks.
To test the trained networks, we use SED and physical properties of 142 galaxies at 0.5 < $z$ < 1 from T12.
Following the T12 work, we chose these two sets of data not only to show the application of SOMs in SED clustering, but also to easily compare both supervised and unsupervised methods.

@@

    K96 used UV-optical spectra of 70 star forming and quiescent nearby galaxies to produce a template that contained 12 types of SEDs.
    These templates were widely used in many studies to determine morphological type of galaxies or properties of specific types of galaxies\citep[e.g.][]{Shakouri16,Paiano16,Laporte16,Holden16}.
    K96 claims that these templates can also be used to classifying the SED of the high redshift galaxies.

    The 12 types (what 12 types? the SEDs? in that case this sentence does not belong here at all) of spectra are divided based on their morphological types for early type galaxies or their extinction for starburst galaxies (Fig.~\ref{fig: k96}). 
    The quiescent group of galaxies includes Bulge (B), Elliptical (E), S0, Sa, Sb, and Sc galaxies.
    Bulge group represents galaxies similar to M31 and M81, which their UV and optical spectroscopy is dominated by the stellar population in their bulges.
    The starburst galaxies are divided into six groups (SB1 to SB6) based on their intrinsic extinctions ($E(B-V)$). 
    As it is clear in the Fig.~\ref{fig: k96}, SB1 galaxies have lower internal extinctions ($E(B-V) \simeq 0.05$), while SB6 galaxies have the highest amount of extinction ($E(B-V) \simeq 0.65$) among starburst galaxies.

    K96 spectra spans from $\sim1200$\AA~to $10000$\AA~with a resolution of $\sim 10$\AA.
    However, in this letter we only use data between $\sim1200$\AA ~to $8000$\AA~to train our networks. 
    This wavelength range was chosen due to availability of flux information in those wavelengths for all 12 types of galaxies.
    In early type galaxies' spectra (B to Sb), the spectrum is redder, and strong absorption lines and 4000\AA~break are distinguishable.
    SEDs of starburst galaxies are more flat on the optical and NIR region than those of the the early types and show strong emission lines.
    For more details on each spectral type, we encourage readers to see K96 and references therein.

 \subsection{SED and Properties of the sample galaxies} 
    T12 selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field.
    For each galaxy, robust spectroscopic redshift and photometry data from the Good-MUSIC catalogue had been known.
    The 142 galaxies were selected in T12 based on the availability of data from HST/ACS, VLA/ISAAC, and {\it Spitzer}/MIPS and IRAC for whole galaxies. 
    Data from these instruments were necessary in order to have a complete picture of stellar population and SFR.
    The photometry data contain information of the galaxies in 10 - 13 filters with the wavelength range of $\sim 0.4-24~\mu$m in the observed frame.
    T12 matched the resolution of the photometry data with K96 data and used these photometry data as inputs for Code Investigating GALaxy Enmission ({\em CIGALE} code;~\citep[][hereafter N09]{Noll09}) to generate the best fitted SED for each galaxy.% as well as some of the physical properties of the galaxies.

    {\em CIGALE} is a valuable tool to investigate the properties of the galaxy using UV to IR wavebands.
    It uses stellar populations, synthetic attenuation and dust emission models, spectral line templates, and active galactic nuclei's optical spectral templates to model SED of the galaxies.
    This code was successfully tested on data from 39 galaxies selected from the Spitzer Infrared Nearby Galaxy Survey (SINGS;~\citep{Kennicutt03}) by N09.
    T12 produced the best SED match, with wavelength interval of 910 to $\sim 8\times10^9$\AA, for each galaxy.
    Assuming decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr, they derived physical properties of galaxies such as age, and stellar mass.
    Some of these properties are shown in Tab.~\ref{tab: props}.
    In the Sec.~\ref{sec: 1D}, we study these properties for each categorization.
    More details on creating SEDs and extracting information about galaxies properties using {\em CIGALE} can be found in N09 and T12.

@@

    For testing the created networks, we use SEDs that were produced by T12. 
    These SEDs are publicly available in the form of flux per rest frame wavelength in a wide range of wavelengths.
    Since we have used the T12 SEDs to test the trained network, we only used the part of the SEDs that have a same wavelength range as K96 templates.

>>>>

\section{DATA}
\label{sec: data}
We use SED templates from K96 to train neural networks.
To test the trained networks, we use SED and physical properties of 142 galaxies at $0.5<z<1$ from T12.
Following the T12 work, we chose these two sets of data not only to show the application of SOMs in SED clustering, but also to easily compare supervised and unsupervised methods.

@@

    K96 used ultraviolet-optical spectra of 70 star forming and quiescent nearby galaxies to produce a set of templates that contained 12 types of SEDs.
    These templates have been widely used in many studies to determine morphological type of galaxies or properties of specific types of galaxies\citep[e.g.][]{Shakouri16,Paiano16,Laporte16,Holden16}.
    K96 stated that these templates can also be used to classify the SED of high-redshift galaxies.

    The 12 templates are divided based on their morphological types for early type galaxies or their extinction for starburst galaxies (Fig.~\ref{fig: k96}). 
    The quiescent group of galaxies includes Bulge (B), Elliptical (E), S0, Sa, Sb, and Sc galaxies.
    The bulge group represents galaxies similar to M31 and M81, whose UV and optical spectra are dominated by their bulge stellar populations.
    The starburst galaxies are divided into six groups (SB1 to SB6) based on their intrinsic extinctions ($E(B-V)$). 
    As Fig.~\ref{fig: k96} shows, SB1 galaxies have lower internal extinctions ($E(B-V) \simeq 0.05$), while SB6 galaxies have the highest amount of extinction ($E(B-V) \simeq 0.65$) among starburst galaxies. 
   In the early type (B to Sb) templates, the spectrum is redder; strong absorption lines and the 4000~\AA~break are distinguishable.
    SEDs of starburst galaxies are flatter in the optical and near-infrared region than those of the early types and show strong emission lines.
    For more details on each spectral type, we encourage readers to see K96 and references therein. 
   The K96 spectra span from $\sim1200$~\AA~to $10000$~\AA~with a resolution of $\sim 10$~\AA.
    However, in this work we only use $\sim1200< \lambda < 8000$~\AA to train our networks; 
    this wavelength range was chosen due to availability of flux information in those wavelengths for all 12 templates.

 \subsection{SED and Properties of the sample galaxies} 
    T12 selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field \citep{}. %PB20160603: need citation here.
    The 142 galaxies were selected based on the availability of photometry from HST/ACS, VLA/ISAAC, and {\it Spitzer}/MIPS and IRAC (10--13 filters with $\sim 0.4<\lambda<24~\mu$m in the observed frame).
   Data from these instruments was necessary in order to have a complete picture of stellar population and star formation rate. 
    For each galaxy, a robust spectroscopic redshift and photometric measurements from the GOODS-MUSYC catalogue \citep{} was available. %PB20160603: need citation here.
   T12 matched the resolution of the photometric data with K96 data %PB20160603: I don't understand what this phrase means
and used the photometry as inputs to the Code Investigating GALaxy Emission ({\em CIGALE});~\citep[][hereafter N09]{Noll09} to generate the best-fit SED for each galaxy.% as well as some of the physical properties of the galaxies.
% PB 20160603: commented out following 3 lines as I don't think this fit well here. Could maybe go somewhere else.    
%    {\em CIGALE} is a valuable tool to investigate the properties of galaxies using ultraviolet to infrared wavebands.
%    It uses stellar populations, synthetic attenuation and dust emission models, spectral line templates, and active galactic nuclei optical spectral templates to model the SEDs of galaxies.
%    This code was successfully tested on data from 39 galaxies selected from the Spitzer Infrared Nearby Galaxy Survey (SINGS;~\citep{Kennicutt03}) by N09.
    T12 produced the best SED match, with wavelength interval of 910 to $\sim 8\times10^9$~\AA, for each galaxy. %PB20160603: 10^9~AA is not a useful unit!
    Assuming decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr, they derived physical properties of the galaxies such as age and stellar mass.
    Some of these properties are shown in Tab.~\ref{tab: props}.
    In Sec.~\ref{sec: 1D}, we study these properties for each category.
    More details on creating SEDs and extracting information about galaxy properties using {\em CIGALE} can be found in N09 and T12.

@@

    For testing the created networks, we use SEDs that were produced by T12. 
    These SEDs are publicly available in the form of flux per rest frame wavelength in a wide range of wavelengths. %PB20160603: available where?
    Since we have used the T12 SEDs to test the trained network, we only used the part of the SEDs that have the same wavelength range as the K96 templates.

%PB20160603: I'm an idiot for not figuring this out sooner, but I think I finally understand what exactly you are doing. For each galaxy the photometric data are fitted with Maraston models by CIGALE, and the best-fit SED is determined. Those SEDs (and not the observed photometric or spectroscopic data) are what's being classified by the SOM in comparison to the K96 templates.
% I think we need a clearer justification of why it's a good idea to do it this way - why use the CIGALE-output SEDs rather than the observed data?  Is it just that we need the continuous wavelnegth overage, or uniform spectral resolution, that the CIGALE-output provides? Are we sure that we are learning something about the galaxies rather than about CIGALE?
